---
title: 'Optical character recognition (OCR)'
output: 
  html_notebook: 
    toc: yes
    toc_depth: 2
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: true
    code_folding: hide
---

In this project, we are going to **focus on the third stage -- post-processing**, which includes two tasks: *error detection* and *error correction*.  

# Step 1 - Load library and source code
```{r, warning=FALSE, message = FALSE}
if (!require("devtools")) install.packages("devtools")
if (!require("pacman")) {
  ## devtools is required
  library(devtools)
  install_github("trinker/pacman")
}
if (!require("zoo")) {
  install.packages("zoo")
}
library(zoo)

if (!require("dplyr")) {
  install.packages("dplyr")
}
library(dplyr)

if (!require("quanteda")) {
  install.packages("quanteda")
}
library(quanteda)

if (!require("caret")) {
  install.packages("caret")
}
library(caret)

pacman::p_load(knitr, readr, stringr, tesseract, vecsets)
file_name_vec <- list.files("../data/ground_truth") #100 files in total
```

# Step 2 - read the files and conduct Tesseract OCR

Although we have processed the Tesseract OCR and save the output txt files in the `data` folder, we include this chunk of code in order to make clear the whole pipeline to you.

```{r, eval=FALSE}
for(i in c(1:length(file_name_vec))){
  current_file_name <- sub(".txt","",file_name_vec[i])
  ## png folder is not provided on github (the code is only on demonstration purpose)
  current_tesseract_txt <- tesseract::ocr(paste("../data/png/",current_file_name,".png",sep=""))
  
  ### clean the tesseract text (separate line by "\n", delete null string, transter to lower case)
  clean_tesseract_txt <- strsplit(current_tesseract_txt,"\n")[[1]]
  clean_tesseract_txt <- clean_tesseract_txt[clean_tesseract_txt!=""]
  
  ### save tesseract text file
  writeLines(clean_tesseract_txt, paste("../data/tesseract/",current_file_name,".txt",sep=""))
}
```

# Step 3 - Error detection

Now, we are ready to conduct post-processing, based on the Tessearct OCR output. First of all, we need to detect errors, or *incorrectly processed words* -- check to see if an input string is a valid dictionary word or if its n-grams are all legal.

The referenced papers are:

1. [Rule-based techniques](http://webpages.ursinus.edu/akontostathis/KulpKontostathisFinal.pdf)

- rules are in the section 2.2 

2. [Letter n-gram](https://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=1672564)

- focus on positional binary digram in section 3-a.error detection

3. Probabilistic techniques -- [SVM garbage detection](https://dl.acm.org/citation.cfm?doid=2034617.2034626)

- features are in section 5 (you can choose not to implement ‘Levenshtein distance’ feature)


In this part, we implement fourteen features in the D-3 paper (SVM classification) and generate the labels for training.

* ###Feature and Label Construction

```{r}
source("../lib/extractFeature.R")
source("../lib/extractLabel.R")

# read 100 files
cat("------------Start Feature and Label Construction------------\n")
dat <- NULL
for (i in 1:length(file_name_vec)) {
  ## set current file name
  current_file_name <- sub(".txt", "", file_name_vec[i])
  ## read the ground truth text
  current_ground_truth_txt <-
    readLines(paste("../data/ground_truth/", current_file_name, ".txt", sep =""), warn = FALSE)
  ## read the tesseract text
  current_tesseract_txt <-
    readLines(paste("../data/tesseract/", current_file_name, ".txt", sep =""), warn = FALSE)
  # tokenize tesseract output
  clean_tesseract_txt <-
    paste(current_tesseract_txt, collapse = " ")
  tesseract_vec <- str_split(clean_tesseract_txt, " ")[[1]]
  # generate feature, label and other information of current file
  current_dat <- NULL
  for (j in 1:length(current_tesseract_txt)) {
    line_info <-
      extractInfo(j, current_tesseract_txt, current_ground_truth_txt)
    current_dat <- as.data.frame(rbind(current_dat, line_info))
  }
  current_dat$file_num <- i
  # merge the feature and label data frame with previous ones
  dat <- rbind(dat, current_dat)
  # print message
  if (i %% 10 == 0) {
    cat(i, "files finished\n")
  }
}
cat("------------Feature and Label Construction Done------------\n")

save(dat, file="../output/data.RData")
```

* ###Cross Validation and SVM Training

Here we cross validate $C$ and $\sigma$ and train the SVM model with each text file group.

```{r}
load("../output/data.RData")
source("../lib/svm.r")

#Defining the groupname in the data column
dat <- dat %>% mutate(group_num = case_when(file_num %in% c(1:10)~"A",
                                            file_num %in% c(11:38)~"B",
                                            file_num %in% c(39:41)~"C",
                                            file_num %in% c(42:68)~"D",
                                            file_num %in% c(69:100)~"E"
))

# Changing the levels of the labels
dat <- dat %>% mutate(label = case_when(label == 1 ~"Correct",
                                        label == 0 ~"Error"))

# Converting labels to factors
dat$label <- factor(dat$label)
# Splitting the dataset by groups
groupsplit <- split(dat,dat$group_num)

# Results
a <- svm.func(groupsplit$A)
b <- svm.func(groupsplit$B)
c <- svm.func(groupsplit$C)
d <- svm.func(groupsplit$D)
e <- svm.func.2(groupsplit$E)

#Saving the outputs
predicted_labels <- rbind(matrix(a$pred),matrix(b$pred),
                          matrix(c$pred),matrix(d$pred),
                          matrix(e$pred))
predicted_labels_list <- list(predicted_labels)

#save(predicted_labels, file = "../output/tempSvmLabels.RData")
#save(predicted_labels.list, file = "../output/listtempSvmLabels.RData")

confs <- cbind(a$conf$overall[1],b$conf$overall[1],
               c$conf$overall[1],d$conf$overall[1],
               e$conf$overall[1])
colnames(confs) <- c("Group 1","Group 2","Group 3","Group 4","Group 5")

detected_tokens <- cbind(rbind(matrix(groupsplit$A$error_token),
                               matrix(groupsplit$B$error_token),
                               matrix(groupsplit$C$error_token),
                               matrix(groupsplit$D$error_token),
                               matrix(groupsplit$E$error_token)), 
                         predicted_labels)

colnames(detected_tokens) <- c("Tesseract_Output","SVM_Label")

# Saving the results
save(confs, file = "../output/accuracy.RData")
save(detected_tokens, file = "../output/detected_tokens.RData")
```

# Step 4 - Error correction

Given the detected word error, in order to find the best correction, we need to generating the candidate corrections: a dictionary or a database of legal n-grams to locate one or more potential correction terms. Then we need invoke some lexical-similarity measure between the misspelled string and the candidates or a probabilistic estimate of the likelihood of the correction to rank order the candidates.

The referenced papers are:

1. [Letter n-gram](https://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=1672564}{positional binary digram)

- focus on section 3-b.error correction

2. Supervised model -- [correction regressor](https://arxiv.org/pdf/1611.06950.pdf)

3. [probability scoring without context](https://link.springer.com/content/pdf/10.1007%2FBF01889984.pdf)

- focus on section 3

4. [probability scoring with contextual constraints](https://link.springer.com/content/pdf/10.1007%2FBF01889984.pdf)

- focus on section 5

5. [topic models](https://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=4377099)

We follow the correction algorithm in C-3.


* ###Generate proposed correction candidates

```{r}
source("../lib/InsertedCandidate.R")
source("../lib/DeletionDatabase.R")
source("../lib/SubstitionDatabase.R")
source("../lib/SearchINDatabase.R")
source("../lib/Clean.R")
source("../lib/FindAllCorrections.R")

load("../output/data.RData")
load("../output/detected_tokens.RData")


  
#### function to see if a char only have letters(SS in Clean.R)
  
## Only choose words
TrueToken <- as.character(dat$true_token)
  
CleanTrueToken <- TrueToken[sapply(TrueToken,SS)]

## lower the letters
lower <- function(char){
  
  #a <- unlist(str_match_all(c,'[a-zA-Z]'))
  #b <- paste(a[1:length(a)],collapse = "")
  c <- tolower(char)
  return(c)
} 


#### All the words in groundtruth(N in training set)
CleanLowTrueToken <- sapply(CleanTrueToken,lower)
  

#####distinct groundtruth(Vocabulary in training set)
V <- unique(CleanLowTrueToken)
  
  #mistakes because of insertion(n dictionary access to see if the nth letter was inserted)
  # InsCan

  #mistakes because of deletion(generate a deletion table and then search)
  # generate the deletion table
  WholeDeletionDatabase <- lapply(V,DeletionDatabasePerWord)
    
    
  # generate the substition table
   WholeSubstitionDatabase <- lapply(V,SubstitionDatabasePerWord)


   ####Try all the corrections for one word
   #AllCorrectionCandidates("mon")
   
```

* ###Find Pr(c) the prior probability


```{r}
source("../lib/PriorForCorrection.R")
### use ELE method

```


* ### Generate the confusion matrix
```{r}
##### Find suitable training set

###### Typos and Corrections
###### First preprocess data for the confusion matrix
###### Find the subset which only has one typo in letters


subdat <- dat[dat$label==0,]


ErrorToken <- as.character(subdat$error_token)
SubTrueToken <- as.character(subdat$true_token)
Index <- sapply(ErrorToken,SS)



CleanErrorToken <- ErrorToken[Index]
CorrespondTrueToken <- SubTrueToken[Index]

CleanLowErrorToken <- sapply(CleanErrorToken,lower)
CorrespondLowTrueToken <- sapply(CorrespondTrueToken,lower)

Index2 <- CleanLowErrorToken!=CorrespondLowTrueToken


FErrorToken <- CleanLowErrorToken[Index2]
FTrueToken <- CorrespondLowTrueToken[Index2]

###Use errors which only have one typo in the letters

# source("../lib/onlyCorrectionForCM.R")
# Index3 <- rep(NA,length(FErrorToken))
# 
# 
# for (i in 1:length(FErrorToken)){
#   Index3[i] <- is.element(FTrueToken[i],AllCorrectionCandidates1(FErrorToken[i]))
#   if (i %% 100 == 0) {cat(i, "words finished\n")}
# }


#save(Index3, file = "../output/IndexWhole.RData")
IndexWhole <- load("../output/IndexWhole.RData")

FinalErrorToken <- FErrorToken[IndexWhole]
FinalTrueToken <- FTrueToken[IndexWhole]




```

```{r}
#######Use FinalErrorToken and FinalTrueToken to generate confusion matrix

####Subsitite initial
  SCM <- matrix(rep(0,26*26),nrow=26,ncol=26)
  SCM <- as.data.frame(SCM,row.names=c("a","b","c","d","e","f","g","h","i","j","k","l","m","n","o",
                                     "p","q","r","s","t","u","v","w","x","y","z"))
  names(SCM)<-c("a","b","c","d","e","f","g","h","i","j","k","l","m","n","o",
          "p","q","r","s","t","u","v","w","x","y","z")
  
####Add initial
  ACM <- matrix(rep(0,27*26),nrow=27,ncol=26)
  ACM <- as.data.frame(ACM,row.names=c("a","b","c","d","e","f","g","h","i","j","k","l","m","n","o","p","q","r","s","t","u","v","w","x","y","z","@"))
  names(ACM)<-c("a","b","c","d","e","f","g","h","i","j","k","l","m","n","o",
          "p","q","r","s","t","u","v","w","x","y","z")
  
#### Del initial
  DCM <- matrix(rep(0,27*26),nrow=27,ncol=26)
  DCM <- as.data.frame(DCM,row.names=c("a","b","c","d","e","f","g","h","i","j","k","l","m","n","o","p","q","r","s","t","u","v","w","x","y","z","@"))
  names(DCM)<-c("a","b","c","d","e","f","g","h","i","j","k","l","m","n","o",
          "p","q","r","s","t","u","v","w","x","y","z")
  
  for (i in 1:length(FinalErrorToken)){
    
    #########Substition typo
    if (nchar(FinalErrorToken[i])==nchar(FinalTrueToken[[i]])){
      id <- which(unlist(strsplit(FinalErrorToken[i], "")) != unlist(strsplit(FinalTrueToken[i], "")))
      row <- substr(FinalErrorToken[i],start=id,stop=id)
      column <- substr(FinalTrueToken[i],start=id,stop=id)
      SCM[row,column] <-SCM[row,column]+1 
    }
    
    
    ####### Insertion typo
    if (nchar(FinalErrorToken[i])>nchar(FinalTrueToken[[i]])){
      if (substr(FinalErrorToken[i],start=1,stop=1)!=substr(FinalTrueToken[i],start=1,stop=1)){
       row <- "@"
       column <- substr(FinalErrorToken[i],start=1,stop=1)
       ACM[row,column] <-ACM[row,column]+1
      }
      else if(sum(unlist(strsplit(substr(FinalErrorToken[i],start=1,stop=nchar(FinalTrueToken[i])),""))!=unlist(strsplit(FinalTrueToken[i], "")))>0
      ){
        id <- min(which(unlist(strsplit(substr(FinalErrorToken[i],start=1,stop=nchar(FinalTrueToken[i])),""))!=unlist(strsplit(FinalTrueToken[i], ""))))
        row <- substr(FinalErrorToken[i],start=id-1,stop=id-1)
        column <- substr(FinalErrorToken[i],start=id,stop=id)
        ACM[row,column] <-ACM[row,column]+1
        
      }
      else{
        id <-nchar(FinalTrueToken[i])
        row <- substr(FinalErrorToken[i],start=id,stop=id)
        column <-  substr(FinalErrorToken[i],start=id+1,stop=id+1)
        ACM[row,column] <-ACM[row,column]+1
        
      }
    }
    
    ####### Deletion typo
    if (nchar(FinalErrorToken[i])<nchar(FinalTrueToken[[i]])){
      if (substr(FinalErrorToken[i],start=1,stop=1)!=substr(FinalTrueToken[i],start=1,stop=1)){
       row <- "@"
       column <- substr(FinalTrueToken[i],start=1,stop=1)
       DCM[row,column] <-DCM[row,column]+1
      }
      else if(sum(unlist(strsplit(substr(FinalTrueToken[i],start=1,stop=nchar(FinalErrorToken[i])),""))!=unlist(strsplit(FinalErrorToken[i], "")))>0
      ){
        id <- min(which(unlist(strsplit(substr(FinalTrueToken[i],start=1,stop=nchar(FinalErrorToken[i])),""))!=unlist(strsplit(FinalErrorToken[i], ""))))
        row <- substr(FinalTrueToken[i],start=id-1,stop=id-1)
        column <- substr(FinalTrueToken[i],start=id,stop=id)
        DCM[row,column] <-DCM[row,column]+1
        
      }
      else{
        id <-nchar(FinalErrorToken[i])
        row <- substr(FinalTrueToken[i],start=id,stop=id)
        column <-  substr(FinalTrueToken[i],start=id+1,stop=id+1)
        DCM[row,column] <-DCM[row,column]+1
        
      }
    }
  }
  


```




```{r}
##### given a word
source("../lib/Chars.R")
source("../lib/FinalFunction.R")

#hh <- rep(NA,length(FinalErrorToken))


#for (i in 13400:length(FinalErrorToken)){
#  hh[i] <- Prob(FinalErrorToken[i])
#  if (i %% 100 == 0) {cat(i, "words finished\n")}
  
  
#}

load("../output/CorrectionList.RData")
FinalTryToken <- hh

#### accuracy just based on these data

acc <- sum(FinalTryToken==FinalTrueToken)/length(FinalTrueToken)
acc

```


* ###Deal with Index
```{r}
dat$SVM_label <- detected_tokens$SVM_Label
dat$ind <- 1:nrow(dat)
In1 <- dat$ind[dat$label==0]
In2 <- In1[Index]
In3 <- In2[Index2]
In4 <- In3[IndexWhole]
dat$corrected_token <- dat$error_token
InPred <- dat$ind[dat$SVM_label=="Error"] 

InFinal <- intersect(In4,InPred)

ini <- 1:39435
InF <- ini[is.element(In4,InFinal)]

dat$corrected_token <- as.character(dat$corrected_token)

dat$corrected_token[InFinal] <- FinalTryToken[InF]

save(dat, file = "../output/FinalDataframe.RData")
```


# Step 5 - Performance measure

The two most common OCR accuracy measures are precision and recall. Both are relative measures of the OCR accuracy because they are computed as ratios of the correct output to the total output (precision) or input (recall). More formally defined,
\begin{align*}
\mbox{precision}&=\frac{\mbox{number of correct items}}{\mbox{number of items in OCR output}}\\
\mbox{recall}&=\frac{\mbox{number of correct items}}{\mbox{number of items in ground truth}}
\end{align*}
where *items* refer to either characters or words, and ground truth is the original text stored in the plain text file. 

Both *precision* and *recall* are mathematically convenient measures because their numeric values are some decimal fractions in the range between 0.0 and 1.0, and thus can be written as percentages. For instance, recall is the percentage of words in the original text correctly found by the OCR engine, whereas precision is the percentage of correctly found words with respect to the total word count of the OCR output. Note that in the OCR-related literature, the term OCR accuracy often refers to recall.

```{r}
load("../output/FinalDataframe.RData")
load("../output/ALLgroundtruth_vec.RData")

# word level evaluation
# old interaction
old_intersect_vec <- dat$error_token[dat$label == 1]
# new interaction
new_intersect_vec <- vecsets::vintersect(tolower(dat$true_token[dat$label == 0]), 
                                         tolower(dat$corrected_token[dat$label == 0]))
new_intersect_vec2 <- c(old_intersect_vec, new_intersect_vec)

OCR_performance_table <- data.frame("Tesseract" = rep(NA,4),
                                    "Tesseract_with_postprocessing" = rep(NA,4))
row.names(OCR_performance_table) <- c("word_wise_recall","word_wise_precision",
                                      "character_wise_recall","character_wise_precision")
OCR_performance_table["word_wise_recall","Tesseract"] <- length(old_intersect_vec)/length(ALLgroundtruth_vec)
OCR_performance_table["word_wise_precision","Tesseract"] <- length(old_intersect_vec)/length(dat$error_token)
OCR_performance_table["word_wise_recall","Tesseract_with_postprocessing"] <- length(new_intersect_vec2)/length(ALLgroundtruth_vec)
OCR_performance_table["word_wise_precision","Tesseract_with_postprocessing"] <- length(new_intersect_vec2)/length(dat$error_token)

# character-level evaluation
# old interaction
ground_truth_vec_char <- str_split(paste(ALLgroundtruth_vec, collapse = ""), "")[[1]]
tesseract_vec_char <- str_split(paste(dat$error_token, collapse = ""), "")[[1]]
old_intersect_vec_char <- str_split(paste(dat$error_token[dat$label == 1], collapse = ""), "")[[1]]
# new interaction
# function used to compare pairs of words in character level
df <- data.frame(true_token=dat$true_token[dat$label == 0], 
                 corrected_token=dat$corrected_token[dat$label == 0])
fun <- function(row) {
  return(vecsets::vintersect(str_split(tolower(row[1]),"")[[1]],
                             str_split(tolower(row[2]),"")[[1]]))
}
correct_char = apply(as.matrix(df), 1, fun)
new_intersect_vec_char <- c(old_intersect_vec_char, unlist(correct_char))

OCR_performance_table["character_wise_recall","Tesseract"] <- length(old_intersect_vec_char)/length(ground_truth_vec_char)
OCR_performance_table["character_wise_precision","Tesseract"] <- length(old_intersect_vec_char)/length(tesseract_vec_char)
OCR_performance_table["character_wise_recall","Tesseract_with_postprocessing"] <- length(new_intersect_vec_char)/length(ground_truth_vec_char)
OCR_performance_table["character_wise_precision","Tesseract_with_postprocessing"] <- length(new_intersect_vec_char)/length(tesseract_vec_char)

kable(OCR_performance_table, caption="Summary of OCR performance")
```

Besides the above required measurement, you are encouraged the explore more evaluation measurements. Here are some related references:

1. Karpinski, R., Lohani, D., & Belaïd, A. *Metrics for Complete Evaluation of OCR Performance*. [pdf](https://csce.ucmss.com/cr/books/2018/LFS/CSREA2018/IPC3481.pdf)

- section 2.1 Text-to-Text evaluation

2. Mei, J., Islam, A., Wu, Y., Moh'd, A., & Milios, E. E. (2016). *Statistical learning for OCR text correction*. arXiv preprint arXiv:1611.06950. [pdf](https://arxiv.org/pdf/1611.06950.pdf)

- section 5, separate the error detection and correction criterions

3. Belaid, A., & Pierron, L. (2001, December). *Generic approach for OCR performance evaluation*. In Document Recognition and Retrieval IX (Vol. 4670, pp. 203-216). International Society for Optics and Photonics. [pdf](https://members.loria.fr/ABelaid/publis/spie02-belaid-pierron.pdf)

- section 3.2, consider the text alignment

# References {-}

1. Borovikov, E. (2014). *A survey of modern optical character recognition techniques*. arXiv preprint arXiv:1412.4183.[pdf](https://pdfs.semanticscholar.org/79c9/cc90b8c2e2c9c54c3862935ea00df7dd56ed.pdf)
(This paper is the source of our evaluation criterion)

2. Kukich, K. (1992). *Techniques for automatically correcting words in text*. Acm Computing Surveys (CSUR), 24(4), 377-439. [pdf](http://www.unige.ch/eti/ptt/docs/kukich-92.pdf)
(This paper is the benchmark review paper)

3. Wudtke, Richard & Ringlstetter, Christoph & U. Schulz, Klaus. (2011). *Recognizing garbage in OCR output on historical documents.* ACM International Conference Proceeding Series. 10.1145/2034617.2034626.

4. Church, K.W. & Gale, W.A. Stat Comput (1991) *Probability Scoring for Error Correction* 1: 93. https://doi.org/10.1007/BF01889984